### 2020-09-12 paper/perfectGraphs.tex
Fixes KT

Do graphs that admit coloring using only $\omega(G)$ color are "simpler" to further analyze? Not necessarily so. Given a graph $G = (V, E)$, $|V| = n$, let us construct a graph $G'$ equal to the union of $G$ and a clique $K_n$. We can see that indeed $\chi(G') = n = \omega(G')$, but it gives us no indication of the structure of $G$ or $G'$. This leads us to the definition of \emph{perfect graphs}

\begin{defn}[perfect graph]
	\label{def:perfectGraph}
	A graph $G$ is \emph{perfect} iff for its every induced subgraph $H$ we have $\chi(H) = \omega(H)$
\end{defn}

@@

\begin{defn}[Berge graph]
	\label{def:bergeGraph}
	A graph $G$ is \emph{Berge} iff both $G$ and $\overline{G}$ have no odd hole as an induced subgraph
\end{defn}

Perfect graphs are interesting not only because of their theoretical properties, but they are also used in other areas of study e.g. integrality of polyhedra \cite{Chvtal1975, Chudnovsky2003}, radio channel assignment problem \cite{McDiarmid99, McDiarmid2000} and appear in the theory of Shannon capacity of a graph \cite{Lovasz1979}. Also, as pointed out in \cite{alfonsinPerfect2001, Chudnovsky2003} algorithms to solve semi-definite programs grew out of the theory of perfect graphs. We will take a look at semi-definite programs and at perfect graph's relation to Shannon capacity in \cref{sec:ellipsoidMethod}.

@@

This theorem is a consequence of a stronger result proven by Lovász:
\begin{theorem}
	\label{thm:omegaalpha}
	A graph $G$ is perfect iff for every induced subgraph $H$, the number of vertices of $H$ is at most $\alpha(H)\omega(H)$. \todo{proof?}
\end{theorem}

@@

In 1961 Berge conjured that a graph is perfect iff it contains no odd hole and no odd antihole in what has become known as a strong perfect graph conjecture. In 2001 Chudnovsky et al. have proven it and published the proof in an over 150 pages long paper \citetitle{MC06} \cite{MC06}.

@@

\subsubsection{2-join, Homogeneous Pair and Skew Partition}
A graph $G$ has a \emph{2-join} if its vertices can be partitioned into sets $V_1$, $V_2$, each of size at least three, and there are nonempty disjoint subsets $A_1, B_1 \subseteq V_1$ and $A_2, B_2 \subseteq V_2$, such that all vertices of $A_1$ are adjacent to all vertices of $A_2$, all vertices of $B_1$ are adjacent to all vertices of $B_2$, and these are the only edges between $V_1$ and $V_2$. When a graph $G$ has a 2-join, it can be decomposed onto two smaller graphs $G_1$, $G_2$, so that $G$ is perfect iff $G_1$ and $G_2$ are perfect \cite{Cornujols1985}.

@@

The proof of \cref{thm:spgt} is a consequence of the \emph{Decomposition theorem}:
\begin{theorem}[Decomposition theorem]
	\label{thm:decomposition}
	Every Berge graph $G$ is basic or has a skew partition or a homogeneous pair, or $G$ or $\overline{G}$ has a 2-join.
\end{theorem}

See \cite{MC06} for the proof of \cref{thm:decomposition} and \cref{thm:spgt}.

@@

Berge graph recognition algorithm could be divided into two parts: first we check if either $G$ or $\overline{G}$ contain any of a number of simple forbidden structures (\cref{SimpleStructures}). If they do, we output that graph is not Berge and stop. Else, we check if there is a near-cleaner for a shortest odd hole (\cref{AmenableHoles}).

@@

A \emph{pyramid} in G is an induced subgraph formed by the union of a triangle \footnote{A triangle is a clique $K_3$.} $\{b_1,b_2,b_3\}$, three paths $\{P_1, P_2, P_3\}$ and another vertex $a$, so that:
\begin{itemize}
	\item $\forall_{1\leq i \leq 3}$ $P_i$ is a path between $a$ and $b_i$
	\item $\forall_{1\leq i < j \leq 3}$ $a$ is the only vertex in both $P_i$ and $P_j$ and $b_ib_j$ is the only edge between $V(P_i)\setminus\{a\}$ and $V(P_j)\setminus\{a\}$.
	\item $a$ is adjacent to at most one of $\{b_1, b_2, b_3\}$.
\end{itemize}

We will say that $a$ can be \emph{linked onto} the triangle $\{b_1, b_2, b_3\}$ \emph{via} the paths $P_1$, $P_2$, $P_3$. Let us notice, that a pyramid is determined by its paths $P_1$, $P_2$, $P_3$.

@@

				\ls assign $P_2$ and $P_3$ in a similar manner
				\ls $good\_pairs_{1,2} \gets \emptyset$ \Comment{see below for definition}
				\mForEach{$m_1 \in M \cup \{b_1\}$} \Comment{calculate good $(1, 2)$-pairs}
					\mIf{$P_1(m_1) \neq \UND$}
						\ls color black the vertices of $M$ that either belong to \label{line:pyramidColor}
						\lsx $P_1(m_1)$ or have a neighbor in $P_1(m_1)$
						\lsx color all other vertices white.
						\mForEach{$m_2 \in M \cup \{b_2\}$}
							\mIf{$P_2(m_2)$ exists and contains no black vertices} \label{line:pyramidColor2}
								\ls add $(m_1, m_2)$ to $good\_pairs_{1,2}$
							\mEndIf
						\mEndFor
					\mEndIf
				\mEndFor
				\ls calculate $good\_pairs_{1,3}$ and $good\_pairs_{2,3}$ in similar way
				\mForEach{triple $m_1, m_2, m_3$ such that $m_i \in M \cup \{b_i\}$} \label{line:m1m2m3}
					\mIf{$\forall_{1\leq i < j \leq 3}$: $(m_i, m_j)$ is a good $(i, j)$-pair}
						\ls \RETURN \TRUE \label{line:pyramidTrue}
					\mEndIf
				\mEndFor
			\mEndIf \label{line:pyramidEnd}
		\mEndFor
	\mEndFor
	\ls \RETURN \FALSE
	\mEndProcedure
\end{algorithmic}

With definitions as above, for $1 \leq i < j \leq 3$, we say that $(m_i, m_j)$ is a \emph{good $(i, j)$-pair}, iff $m_i \in M \cup \{b_i\}$, $m_j \in M \cup \{b_j\}$, $P_i(m_i)$ and $P_j(m_j)$ both exist, and the sets $V(P_i(m_i))$,$V(P_j(m_j))$ are both disjoint and $b_ib_j$ is the only edge between them.

It is easy to see, that if \textsc{Contains-Pyramid($G$)} outputs that $G$ contains a pyramid, it indeed does -- when we return in line \ref{line:pyramidTrue} $a$ found in line \ref{line:a} can be linked into a triangle $b_1, b_2, b_3$ it was found for via paths $P_1(m_1), P_2(m_2), P_3(m_3)$ for $m_1$, $m_2$, $m_3$ from line \ref{line:m1m2m3}. The proof of the converse is rather technical and we refer to \cite{MC05} for it.

@@

Five vertices $v_1, \ldots, v_5$ and a path $P$ form a \emph{jewel} iff:

\begin{itemize}
	\item $v_1, \ldots, v_5$ are distinct vertices.
	\item $v_1v_2, v_2v_3, v_3v_4, v_4v_5, v_5v_1$ are edges.
	\item $v_1v_3, v_2v_4, v_1,v_4$ are nonedges.
	\item $P$ is a path between $v_1$ and $v_4$, such that $v_2, v_3, v_5$ have no neighbors in its inside.
\end{itemize}

@@

The following algorithm with running time of $O(|V(G)|^6)$ checks whether $G$ contains a configuration of type $T_3$:

@@

	\noindent Output: Returns whether $G$ contains a configuration of type $T_3$ as an induced subgraph.
\end{alg}
% \begin{algorithmic}
% 	\mProcedure{Contains-T3}{$G$}
% 	\mForEach{$v_1, v_2, v_5 \in V(G)$, so that $v_1v_2$ is an edge and $v_1v_5, v_2v_5$ are nonedges}
% 	\mEndFor
% 	\mEndProcedure
% \end{algorithmic}
% \begin{algorithmic}[1]
% 	\mProcedure{Contains-Pyramid}{$G$}
% 	\ls \RETURN \FALSE
% 	\mEndProcedure
% \end{algorithmic}

% \begin{algtext2}

	For each triple $v_1, v_2, v_5$ of vertices such that $v_1v_2$ is an edge and $v_1v_5, v_2v_5$ are nonedges find the set $Y$ of all $\{v_1, v_2, v_5\}$-complete vertices. For each anticomponent $X$ of $Y$ find the maximal connected subset $F'$ containing $v_5$ such that $v_1, v_2$ have no neighbors in $F'$ and no vertex of $F'\setminus\{v_5\}$ is $X$-complete. Let $F$ be the union of $F'$ and the set of all $X$-complete vertices that have a neighbor in $F'$ and are nonadjacent to all of $v_1, v_2$ and $v_5$.

	Then, for each choice of $v_4$ that is adjacent to $v_1$ and not to $v_2$ and $v_5$ and has a neighbor in $F$ (call it $v_6$) and a nonneibhbor in $X$, we test whether there is a vertex $v_3$, adjacent to $v_2, v_4, v_5$ and not to $v_1$, with a nonneibhbor in $X$. If there is such a vertex $v_3$, find $P$ -- a path from $v_6$ to $v_5$ with interior in $F'$ and return that $v_1, \ldots v_6, P, X$ is a configuration of type $\T_3$. If we exhaust our search and find none, report that graph does not contain it.
% \end{algtext2}

To see that the \cref{alg:t3} has a running time of $O(|V(G)|^6)$, let us note that for each triple $v_1, v_2, v_5$ we examine, of which there are $O(|V(G)|^3)$, there are linear many choices of $X$, each taking $O(|V(G)|^2)$ time to process and generating a linear many choices of $v_4$ which take a linear time to process in turn. This gives us the total running time of $O(|V(G)|^6)$.

We will skip the proof that each graph containing $\T_3$ is not Berge. See section 6 6.7 of \cite{MC05} for the proof.

@@

@@

With \cref{thm:amenableHoles} we can describe the rest of the algorithm.

@@

	\noindent Output: $O(|V(G)|^5)$ subsets of $V(G)$, such that if $C$ is an amenable hole in $G$, then one of the subsets is a near-cleaner for $C$.
\end{alg}
\begin{algtext2}
	We will call a triple $(a, b, c)$ of vertices \emph{relevant} if $a, b$ are distinct (possibly $c \in \{a, b\}$) and $G[\{a,b,c\}]$ is an independent set.

@@

\begin{alg}[Test possible near clener, 5.1 of \cite{MC05}]
	\label{alg:testNearCleaner}
	Input: A graph $G$ containing no simple forbidden structure, and a subset $X \subseteq V(G)$.

	\noindent Output: Determines one of the following:
	\begin{itemize}
		\item $G$ has an odd hole
		\item There is no shortest odd hole $C$ such that $X$ is a near-cleaner for $C$.
	\end{itemize}
\end{alg}
\begin{algtext2}
	For every pair $x, y \in V(G)$ of distinct vertices find shortest path $R(x, y)$ between $x, y$ with no internal vertex in $X$. If there is one, let $r(x, y)$ be its length, if not, let $r(x, y)$ be infinite.

	For all $y_1 \in V(G)\setminus X$ and all 3-vertex paths $x_1-x_2-x_3$ of $G\setminus y_1$ we check the following:
	\begin{itemize}
		\item $R(x_1, y_1), R(x_2, y_2)$ both exist -- define $y_2$ as the neighbor of $y_1$ in $R(x_2, y_1)$.
		\item $r(x_2, y_1) = r(x_1, y_1) + 1 = r(x_1, y_2)$ ($=n$ say)
		\item $r(x_3, y_1), r(x_3, y_2) \geq n$
	\end{itemize}

>>>>

Do graphs that admit coloring using only $\omega(G)$ color are "simpler" to further analyze? Not necessarily so. Given a graph $G = (V, E)$, $|V| = n$, let us construct a graph $G'$ as the union of $G$ and a clique $K_n$. We can see that indeed $\chi(G') = \omega(G') = n$, but it gives us no indication of the structure of $G$ or $G'$. This leads us to the hereditary definition of \emph{perfect graphs}.

\begin{defn}[perfect graph]
	\label{def:perfectGraph}
	A graph $G$ is \emph{perfect} if and only if for its every induced subgraph $H$ we have $\chi(H) = \omega(H)$.
\end{defn}

@@

\begin{defn}[Berge graph]
	\label{def:bergeGraph}
	A graph $G$ is \emph{Berge} if and only if both $G$ and $\overline{G}$ have no odd hole as an induced subgraph.
\end{defn}

Perfect graphs are interesting not only because of their theoretical properties, but they are also used in other areas of study e.g. integrality of polyhedra \cite{Chvtal1975, Chudnovsky2003}, radio channel assignment problem \cite{McDiarmid99, McDiarmid2000} and appear in the theory of Shannon capacity of a graph \cite{Lovasz1979}. Also, as pointed out in \cite{alfonsinPerfect2001, Chudnovsky2003} algorithms to solve semi-definite programs grew out of the theory of perfect graphs. We will take a look at semi-definite programs and at perfect graph's relation to Shannon capacity in \cref{sec:ShannonCapacity}.

@@

This theorem is a consequence of a stronger result proven by Lovász:
\begin{theorem}
	\label{thm:omegaalpha}
	A graph $G$ is perfect if and only if for every induced subgraph $H$, the number of vertices of $H$ is at most $\alpha(H)\omega(H)$. \todo{proof!}
\end{theorem}

@@

In 1961 Berge conjured that a graph is perfect if and only if it contains no odd hole and no odd antihole in what has become known as a strong perfect graph conjecture. In 2001 Chudnovsky et al. have proven it and published the proof in an over 150 pages long paper \citetitle{MC06} \cite{MC06}.

@@

\subsubsection{2-join, Homogeneous Pair and Skew Partition}
A graph $G$ has a \emph{2-join} if its vertices can be partitioned into sets $V_1$, $V_2$, each of size at least three, and there are nonempty disjoint subsets $A_1, B_1 \subseteq V_1$ and $A_2, B_2 \subseteq V_2$, such that all vertices of $A_1$ are adjacent to all vertices of $A_2$, all vertices of $B_1$ are adjacent to all vertices of $B_2$, and these are the only edges between $V_1$ and $V_2$. When a graph $G$ has a 2-join, it can be decomposed onto two smaller graphs $G_1$, $G_2$, so that $G$ is perfect if and only if $G_1$ and $G_2$ are perfect \cite{Cornujols1985}.

@@

The proof of \cref{thm:spgt} is a consequence of the \emph{Decomposition theorem}:
\begin{theorem}[Decomposition theorem]
	\label{thm:decomposition}
	Every Berge graph $G$ is basic or has a skew partition or a homogeneous pair, or either $G$ or $\overline{G}$ has a 2-join.
\end{theorem}

See \cite{MC06} for the proof of \cref{thm:spgt} and \cref{thm:decomposition}.

@@

Berge graph recognition algorithm (later called CCLSV from the names of its authors) could be divided into two parts: first we check if either $G$ or $\overline{G}$ contain any of a number of simple forbidden structures (\cref{SimpleStructures}). If they do, we output that graph is not Berge and stop. Else, we check if there is a near-cleaner for a shortest odd hole (\cref{AmenableHoles}).

@@

A \emph{pyramid} in G is an induced subgraph formed by the union of a triangle \footnote{A triangle is a clique $K_3$.} $\{b_1,b_2,b_3\}$, three paths $\{P_1, P_2, P_3\}$ and another vertex $a$, so that:
\begin{itemize}
	\item $\forall_{1\leq i \leq 3}$ $P_i$ is a path between $a$ and $b_i$,
	\item $\forall_{1\leq i < j \leq 3}$ $a$ is the only vertex in both $P_i$ and $P_j$ and $b_ib_j$ is the only edge between $V(P_i)\setminus\{a\}$ and $V(P_j)\setminus\{a\}$,
	\item $a$ is adjacent to at most one of $\{b_1, b_2, b_3\}$.
\end{itemize}

We will say that $a$ can be \emph{linked onto} the triangle $\{b_1, b_2, b_3\}$ \emph{via} the paths $P_1$, $P_2$, $P_3$. Let us notice, that a pyramid is uniquely determined by its paths $P_1$, $P_2$, $P_3$.

@@

				\ls assign $P_2$ and $P_3$ in a similar manner
				\ls $good\_pairs_{1,2} \gets \emptyset$ \Comment{see below for definition}
				\mForEach{$m_1 \in M \cup \{b_1\}$} \Comment{calculate good $(1, 2)$-pairs}
					\mIf{$P_1(m_1) \neq \UND$}
						\ls color black the vertices of $M$ that either belong to \label{line:pyramidColor}
						\lsx $P_1(m_1)$ or have a neighbor in $P_1(m_1)$
						\lsx color all other vertices white.
						\mForEach{$m_2 \in M \cup \{b_2\}$}
							\mIf{$P_2(m_2)$ exists and contains no black vertices \lsx} \label{line:pyramidColor2}
								\ls add $(m_1, m_2)$ to $good\_pairs_{1,2}$
							\mEndIf
						\mEndFor
					\mEndIf
				\mEndFor
				\ls calculate $good\_pairs_{1,3}$ and $good\_pairs_{2,3}$ in similar way
				\mForEach{triple $m_1, m_2, m_3$ such that $m_i \in M \cup \{b_i\}$} \label{line:m1m2m3}
					\mIf{$\forall_{1\leq i < j \leq 3}$: $(m_i, m_j)$ is a good $(i, j)$-pair}
						\ls \RETURN \TRUE \label{line:pyramidTrue}
					\mEndIf
				\mEndFor
			\mEndIf \label{line:pyramidEnd}
		\mEndFor
	\mEndFor
	\ls \RETURN \FALSE
	\mEndProcedure
\end{algorithmic}

With definitions as above, for $1 \leq i < j \leq 3$, we say that $(m_i, m_j)$ is a \emph{good $(i, j)$-pair}, if and only if $m_i \in M \cup \{b_i\}$, $m_j \in M \cup \{b_j\}$, $P_i(m_i)$ and $P_j(m_j)$ both exist, and the sets $V(P_i(m_i))$,$V(P_j(m_j))$ are both disjoint and $b_ib_j$ is the only edge between them. In line \ref{line:pyramidColor} we color vertices of $P_1(m_1)$ black, so that for each $m_2$ we can check if paths $P_1(m_1)$ and $P_2(m_2)$ are disjoint in $O(|V|)$ time.

It is easy to see, that if \textsc{Contains-Pyramid($G$)} outputs that $G$ contains a pyramid, it indeed does -- when we return in line \ref{line:pyramidTrue} the vertex $a$ found in line \ref{line:a} can be linked into a triangle $b_1, b_2, b_3$ via paths $P_1(m_1), P_2(m_2), P_3(m_3)$ for $m_1$, $m_2$, $m_3$ from line \ref{line:m1m2m3}. The proof of the converse is rather technical and we refer to \todo{dokładny nr twierdzenia} \cite{MC05} for it.

@@

Five vertices $v_1, \ldots, v_5$ and a path $P$ form a \emph{jewel} if and only if:

\begin{itemize}
	\item $v_1, \ldots, v_5$ are distinct vertices,
	\item $v_1v_2, v_2v_3, v_3v_4, v_4v_5, v_5v_1$ are edges,
	\item $v_1v_3, v_2v_4, v_1,v_4$ are nonedges,
	\item $P$ is a path between $v_1$ and $v_4$, such that $v_2, v_3, v_5$ have no neighbors in its inside.
\end{itemize}

@@

The following algorithm with running time of $O(|V|^6)$ checks whether $G$ contains a configuration of type $\T_3$:

@@

	\noindent Output: Returns whether $G$ contains a configuration of type $T_3$ as an induced subgraph.
\end{alg}

\begin{algorithmic}[1]
	\mProcedure{Contains-T3}{$G$}
	\mForEach{$v_1, v_2, v_5 \in V(G)$, so that $v_1v_2$ is an edge \AND
		\lsx $v_1v_5, v_2v_5$ are nonedges}
		\ls $Y \gets$ the set of all $\{v_1, v_2, v_5\}$-complete vertices.
		\mForEach{$X$ -- an anticomponent of $Y$}
			\ls $F' \gets$ maximal connected subset containing $v_5$, such that $v_1, v_2$
			\lsx have no neighbors in $F'$ and no vertex of $F'\setminus\{v_5\}$ is $X$-complete.
			\ls $F'' \gets$ the set of all $X$-complete vertices that have a neighbor in 
			\lsx $F'$ and are nonadjacent to all of $v_1, v_2$ and $v_5$
			\ls $F \gets F' \cup F''$
			\mForEach{$v_4 \in V(G) \setminus\{v_1, v_2, v_5\}$, such that $v_4$ is adjacent to $v_1$
			\lsx and not to $v_2$ and $v_5$}
				\mIf{$v_4$ has a neighbor in $F$ and a nonneibhbor in $X$}
					\ls $v_6 \gets$ a neighbor of $v_4$ in $F$
					\mForEach{$v_3 \in V(G) \setminus\{v_1, v_2, v_4, v_5, v_6\}$}
						\mIf{$v_3$ is adjacent to $v_2, v_4, v_5$ and not adjacent to $v_1$ \lsx}
							\ls $P \gets$ a path from $v_6$ to $v_5$ with interior in $F'$
							\ls \RETURN \TRUE \Comment{$v_1, \ldots v_6, P, X$ is a $\T_3$}
						\mEndIf
					\mEndFor
				\mEndIf
			\mEndFor
		\mEndFor
	\mEndFor
	\ls \RETURN \FALSE
	\mEndProcedure
\end{algorithmic}

We will skip the proof that each graph containing $\T_3$ is not Berge, as it is quite technical. See section 6.7 of \cite{MC05} for the proof.

\begin{theorem}

\end{theorem}

To see that the \cref{alg:t3} has a running time of $O(|V|^6)$, let us note that for each triple $v_1, v_2, v_5$ we examine, of which there are $O(|V|^3)$, there are linear many choices of $X$, each taking $O(|V|^2)$ time to process and generating a linear many choices of $v_4$ which take a linear time to process in turn. This gives us the total running time of $O(|V|^6)$.

.

@@

First, let us introduce a few new definitions.

\begin{defn}[C-major vertices]
  Given a shortest odd hole $C$ in $G$, a node $v \in V(G) \setminus V(C)$ is $C$-major if the set of its neighbors in $C$ is not contained in any 3-node path of $C$.
  \TODO{a picture of this, clean odd hole, amenable hole}
\end{defn}

\begin{defn}[clean odd hole]
  An odd hole $C$ of $G$ is \emph{clean} if no vertex in $G$ is $C$-major.
\end{defn}

\begin{defn}[cleaner]
  Given a shortest odd hole $C$ in $G$, a subset $X \subseteq V(G)$ is a \emph{cleaner for $C$} if $X \cap V(C) = \emptyset$ and every $C$-major vertex belongs to $X$.
\end{defn}

Let us notice, that if $X$ is a cleaner for $C$ then $C$ is a clean hole in $G \setminus X$.

\begin{defn}[near-cleaner]
  Given a shortest odd hole $C$ in $G$, a subset $X \subseteq V(G)$ is a \emph{near-cleaner for $C$} if $X$ contains all $C$-major vertices and $X \cap V(C)$ is a subset of vertex set of some 3-node path of $C$.
\end{defn}

\begin{defn}[amenable odd hole]
  An odd hole $C$ of $G$ is \emph{amenable} if it is a shortest off hole in $G$, it is of length at least 7 and for every anticonnected set $X$ of $C$-major vertices there is a $X$-complete edge in $C$.
\end{defn}

@@

With \Cref{thm:amenableHoles} we can describe the rest of the algorithm.

@@

	\noindent Output: $O(|V|^5)$ subsets of $V(G)$, such that if $C$ is an amenable hole in $G$, then one of the subsets is a near-cleaner for $C$.
\end{alg}
\begin{algtext2}
	We will call a triple $(a, b, c)$ of vertices \emph{relevant} if $a \neq b$ (but possibly $c \in \{a, b\}$) and $G[\{a,b,c\}]$ is an independent set.

@@

\begin{alg}[Test possible near cleaner, 5.1 of \cite{MC05}]
	\label{alg:testNearCleaner}
	Input: A graph $G$ containing no simple forbidden structure, and a subset $X \subseteq V(G)$.

	\noindent Output: Determines one of the following:
	\begin{itemize}
		\item $G$ has an odd hole
		\item There is no shortest odd hole $C$ such that $X$ is a near-cleaner for $C$.
	\end{itemize}
\end{alg}
\begin{algtext2}
	For every pair $x, y \in V(G)$ of distinct vertices find shortest path $R(x, y)$ between $x, y$ with no internal vertex in $X$. If there is one, let $r(x, y)$ be its length, if not, let $r(x, y) = \infty$.

	For all $y_1 \in V(G)\setminus X$ and all 3-vertex paths $x_1-x_2-x_3$ of $G\setminus y_1$ we check the following:
	\begin{itemize}
		\item $R(x_1, y_1), R(x_2, y_2)$ both exist -- define $y_2$ as the neighbor of $y_1$ in $R(x_2, y_1)$.
		\item $r(x_2, y_1) = r(x_1, y_1) + 1 = r(x_1, y_2)$ ($=n$ say) 
		\item $r(x_3, y_1), r(x_3, y_2) \geq n$
	\end{itemize}
	\TODO{moze raczej $min(r(x_3, y_1), r(x_3, y_2)) = r(x_2, y_1) = r(x_1, y_2) = r(x_1, y_1) + 1$?}
